### 2014-03-07 src/methodology.Rnw
update

While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant. For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(line, 1/64)} is less than 1. Our choices at this point are 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).

>>>>

While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant. For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(line, 1/64)} is less than 1. We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).

\subsubsection{Lines per element}
Our previous research~\cite{gopinath2014code} found that statement coverage was highly correlated with mutation coverage for a project. This immediately suggests that perhaps choosing one mutant per line may be sufficient to achieve a close approximation of the final mutation score. Further, statement deletion has been researched previously~\cite{untch2009onreduced,deng2013empirical} and has been found to reduce the number of mutants well, without an appreciable decrease in accuracy. This also provides a nice comparison with similar number of mutants between operator selection and random sampling of mutants.
